\noindent\textcolor{themecolor}{\textbf{WORK EXPERIENCE}}

\vspace{2mm}
\hrule
\vspace{3mm}

\begin{verbose}{Flextock, Egypt}{January 2024 - Present}{Senior Software Engineer I}
    \noindent $\cdot$ Designing and developing new Flextock products.
\end{verbose}
\begin{verbose}{}{January 2023 - Present}{Software Engineer II}
    \noindent $\cdot$ Designing, developing, maintaining, monitoring and handling incidents of Flextock's billing system.

    \noindent $\cdot$ Worked on the authentication \& authorization of Alkaseba Platform.

    \noindent $\cdot$ Worked on designing new components for Flextock's architecture.
\end{verbose}
\begin{verbose}{}{April 2021 - January 2023}{Software Engineer}
    \noindent $\cdot$ Worked on splitting the billing system to a standalone service.

    \noindent $\cdot$ Worked on the developing and maintaining the first versions of Flextock's billing system.

    \noindent $\cdot$ Worked on developing the first version of Flextock's ticketing system.
\end{verbose}

\vspace{3mm}

\begin{verbose}{CSTeam, Egypt}{September 2019 - February 2020}{Software Engineer}
    \noindent $\cdot$ Worked on developing frontend for CSTeam mobile App using Flutter and Uncle Bob's Clean Architecture.

    \noindent $\cdot$ Performed unit and integration testing.
    
    \noindent $\cdot$ Applied BLoC pattern.
    
    \noindent $\cdot$ Worked in an agile environment.
\end{verbose}

\vspace{3mm}

\begin{verbose}{Multi-Core, Egypt}{September 2018 - January 2019}{Software Engineer}
    \noindent $\cdot$ Worked on developing frontend for TeachersHub mobile App using Flutter.

    \noindent $\cdot$ Worked on deploying the App to Google Play Store.
\end{verbose}

\vspace{3mm}

\begin{verbose}{Orange Business Services, Egypt}{August 2018 - September 2018}{Software Developer Intern}
    \noindent $\cdot$ Developed a Web App that facilitates the work of Level 2 Support Engineers for certain incidents.

    \noindent $\cdot$ Worked on maintaining an existing Web App.
\end{verbose}

